---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.retina = 2
)
library(jwdid)
```

# jwdid

<!-- badges: start -->
[![R-CMD-check](https://github.com/ura8107/gravitydid/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ura8107/gravitydid/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://opensource.org/license/mit)
<!-- badges: end -->

`jwdid` estimates extended two-way fixed-effects (ETWFE)
difference-in-differences models for staggered interventions. It brings the
released Stata `jwdid` workflow to R: flexible treatment-effect heterogeneity,
never- or not-yet-treated controls, anticipation, nonlinear outcomes,
continuous treatment intensity, and `estat`-style aggregation.

## Installation

Install the development version from GitHub:

```r
# install.packages("pak")
pak::pak("ura8107/gravitydid")
```

## Quick start

The example uses the public `mpdta` county-level employment panel distributed
with the `did` package.

```{r quick-start}
data("mpdta", package = "did")

fit <- jwdid(
  lemp ~ 1,
  data = mpdta,
  ivar = countyreal,
  tvar = year,
  gvar = first.treat,
  never = TRUE
)

jwdid_simple(fit)
```

Event-study aggregation returns one estimate per relative period:

```{r event-table}
event <- jwdid_event(fit, window = c(-3, 3), pretrend = TRUE)
event
event$pretrend
```

```{r event-plot, fig.width=7, fig.height=4.5}
plot(
  event,
  style = "pointrange",
  pre = list(colour = "#0072B2"),
  post = list(colour = "#D55E00")
)
```

## Choosing an R DiD implementation

| Package | Primary approach | `jwdid`-style option parity | Nonlinear ETWFE | Aggregation |
|---|---|---:|---:|---|
| `jwdid` | Wooldridge ETWFE | Broad | Poisson, logit, probit | simple, cohort, calendar, event, ATT(g,t) |
| `etwfe` | Wooldridge ETWFE | Core estimator | Via package interface | marginal effects |
| `did` | Callaway--Sant'Anna group-time ATT | Different interface | No | group, calendar, event |

The packages answer related questions with different estimands and
implementations. Matching option names does not by itself make estimates from
different methods numerically identical.

## Validation

The implementation is covered by regression, error-contract, nonlinear-model,
aggregation, plotting, and Stata-parity tests. CI runs `R CMD check` on Linux,
macOS, and Windows. Numerical validation is reported only for fixtures and
reference outputs included in the test suite; it is not a claim that every
possible Stata model specification is identical.

## References

- Wooldridge, J. M. (2021). *Two-Way Fixed Effects, the Two-Way Mundlak
  Regression, and Difference-in-Differences Estimators*.
  <https://doi.org/10.2139/ssrn.3906345>
- Wooldridge, J. M. (2023). Simple approaches to nonlinear
  difference-in-differences with panel data. *The Econometrics Journal*, 26,
  C31--C66. <https://doi.org/10.1093/ectj/utad016>
- Callaway, B. and Sant'Anna, P. H. C. (2021).
  Difference-in-Differences with multiple time periods.
  *Journal of Econometrics*, 225, 200--230.
  <https://doi.org/10.1016/j.jeconom.2020.12.001>
