---
title: "Gravity and trade applications"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Gravity and trade applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(jwdid)
set.seed(8107)
```

Trade flows and other nonnegative outcomes can be estimated with the Poisson
backend. The small balanced panel below mimics bilateral flows after an
agreement begins for two cohorts.

```{r simulate}
pairs <- 1:120
years <- 2015:2022
trade <- expand.grid(pair_id = pairs, year = years)
trade$agreement_year <- c(rep(2018, 40), rep(2020, 40), rep(0, 40))[trade$pair_id]
trade$log_distance <- log(runif(length(pairs), 200, 8000))[trade$pair_id]
treated <- trade$agreement_year > 0 & trade$year >= trade$agreement_year
pair_effect <- rnorm(length(pairs), 1.5, 0.3)[trade$pair_id]
year_effect <- 0.03 * (trade$year - min(years))
trade$flow <- rpois(
  nrow(trade),
  exp(pair_effect + year_effect - 0.12 * trade$log_distance + 0.25 * treated)
)
head(trade)
```

`method = "fepois"` absorbs pair and year fixed effects. Never-treated pairs
form the comparison group.

```{r poisson}
m <- jwdid(
  flow ~ log_distance, trade,
  ivar = pair_id, tvar = year, gvar = agreement_year,
  method = "fepois", never = TRUE
)
jwdid_simple(m)
jwdid_event(m, window = c(-2, 3))
```

For a continuous treatment, supply `trtvar` in place of a treatment cohort.
`jwdid_aggte(..., asis = TRUE)` then contrasts each observed intensity with
zero. The estimand differs from the binary agreement example, so its scale
should be stated explicitly when results are reported.
