---
title: "Getting started with jwdid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with jwdid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(jwdid)
```

`jwdid()` estimates Wooldridge's extended two-way fixed-effects model. This
vignette uses the `mpdta` panel shipped with the suggested `did` package.

```{r data}
data("mpdta", package = "did")
str(mpdta[c("countyreal", "year", "first.treat", "lemp")])
```

Fit a cohort-by-time model using never-treated counties as controls:

```{r fit}
m <- jwdid(
  lemp ~ 1, mpdta,
  ivar = countyreal, tvar = year, gvar = first.treat,
  never = TRUE
)
m
```

The overall ATT is a weighted average of treated observations.

```{r simple}
jwdid_simple(m)
```

Event-study aggregation supports period windows and a joint pre-trend test.

```{r event}
event <- jwdid_event(m, window = c(-3, 3), pretrend = TRUE)
event
event$pretrend
```

```{r plot, fig.width=7, fig.height=4.5}
if (requireNamespace("ggplot2", quietly = TRUE)) {
  plot(event, style = "pointrange")
}
```

The R default `anticipation = 0` corresponds to omitting Stata's option.
R `anticipation = k` corresponds to Stata `anticipation(k + 1)`.
