---
title: "Migrating from Stata jwdid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Migrating from Stata jwdid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(jwdid)
```

The R interface follows the released Stata command while using formulas and
ordinary R vectors.

| Stata | R |
|---|---|
| `jwdid y x, ivar(i) tvar(t) gvar(g)` | `jwdid(y ~ x, data, ivar = i, tvar = t, gvar = g)` |
| `never` | `never = TRUE` |
| `anticipation(2)` | `anticipation = 1` |
| `estat event, window(-3 3)` | `jwdid_event(m, window = c(-3, 3))` |
| `estat event, pretrend` | `jwdid_event(m, pretrend = TRUE)` |

Here is a complete translation:

```{r fit}
data("mpdta", package = "did")
m <- jwdid(
  lemp ~ 1, mpdta,
  ivar = countyreal, tvar = year, gvar = first.treat,
  never = TRUE
)
estat(m, type = "simple")
jwdid_event(m, window = c(-3, 3), pretrend = TRUE)
```

`jwdid_aggte()` is the explicit post-estimation entry point. The bare name
`aggte()` is intentionally not exported because `did` exports an unrelated
function with that name. Typed wrappers include `jwdid_simple()`,
`jwdid_group()`, `jwdid_calendar()`, `jwdid_event()`, `jwdid_attgt()`, and
`jwdid_any()`.

For parity with released Stata `jwdid`, `hettype_ll` also applies under the
not-yet-treated control mode. This preserves an upstream macro-expansion
behavior intentionally and is covered by regression tests.
